%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventrydetailed
    {Android/iOS Developer} % Job title
    {Orange} % Organization
    {Tunis, Tunisia} % Location
    {Aug. 2016 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created fully functional applications for Android and iOS \& wrote clean, clear, efficient, well-tested, and maintainable code.}
        \item {Contribute and participate in new feature/product specifications.}
        \item {Supervised trainees in their graduation projects.}
        \item {Provided training sessions in various fields and languages (Swift, Kotlin, Git...).}
      \end{cvitems}
    }
    {Kotlin, Java, Swift, Objective-C, Git, Scrum, Tuleap, Gitlab} % Technologies
    
%---------------------------------------------------------
  \cventrydetailed
    {Intern - Graduation Project} % Job title
    {Orange} % Organization
    {Tunis, Tunisia} % Location
    {Feb. 2016 - Jul. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed universal iOS application (iPhone/iPad) which citizens get instant informations and statistics about their municipalities}
        \item {Developed a back-end (Laravel)}
      \end{cvitems}
    }
    {Objective-C, Java, Git, Laravel, Scrum, ActiveColab, Gitlab} % Technologies

%---------------------------------------------------------
  \cventrydetailed
    {Intern} % Job title
    {Ciblo.net} % Organization
    {Tunis, Tunisia} % Location
    {Feb. 2016 - Mar. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {E-COM: Android/Backend e-commerce application based on CMS
        	(prestashop) that allows user to interact with site contents from the
        	android application with the ability to manage it from the backend}
      \end{cvitems}
    }
    {Android, Java, Prestashop, PHP, REST-API, Git} % Technologies
%---------------------------------------------------------
  \cventrydetailed
    {Intern} % Job title
    {Education4Sight} % Organization
    {Tunis, Tunisia} % Location
    {Jun. 2015 - Jul. 2015} % Date(s)
    {
    	\begin{cvitems} % Description(s) of tasks/responsibilities
    		\item {EDLIGO - Developed an android application for managing teachers lessons and notes.}
    	\end{cvitems}
    }
    {Android, Java, PHP, REST-API, Git} % Technologies

%---------------------------------------------------------
\end{cventries}
